\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

% Enable hyperlinks
\setupinteraction[state=start, color=middleblue]

\setuppapersize [letter][letter]
\setuplayout    [width=middle,  backspace=1.5in, cutspace=1.5in,
                 height=middle, topspace=0.75in, bottomspace=0.75in]

\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt]

\setupwhitespace[medium]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfc]
\setuphead[subsection]   [style=\tfb]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

\definedescription
  [description]
  [headstyle=bold, style=normal, location=hanging, width=broad, margin=1cm]

\setupitemize[autointro]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\blank[medium]},
   after={\blank[medium]},
   indentnext=no,
  ]


\starttext

\section[james-tomasino]{James Tomasino}

\subsection[technology-director-csm]{Technology Director, CSM}

\startitemize[packed]
\item
  Phone: \useURL[url1][tel://410-929-3008][][410.929.3008]\from[url1]
\item
  Email:
  \useURL[url2][mailto://resume@jamestomasino.com][][resume@jamestomasino.com]\from[url2]
\item
  Labs:
  \useURL[url3][http://labs.tomasino.org][][labs.tomasino.org]\from[url3]
\item
  Blog:
  \useURL[url4][http://tomasinoblog.com][][tomasinoblog.com]\from[url4]
\item
  Github:
  \useURL[url5][http://github.com/jamestomasino][][jamestomasino]\from[url5]
\item
  Twitter:
  @\useURL[url6][http://twitter.com/mr_ino][][mr_ino]\from[url6]
\stopitemize

\subsection[summary]{Summary}

Lead interactive developer and designer with broad experience in a
variety of software packages, languages, and techniques. Particular
affinity for coding and architecting complex interactive experiences.
Interested in opportunities with management of interactive and creative
teams while providing architectural support during development.

\subsection[specialties]{Specialties}

Leading a diverse team of developers via cross-training, cooperation and
skill building. Flash Actionscript 2 & 3, XML, HTML, CSS, JavaScript,
Interactive Design, Usability, Experience Design, Object Oriented
Design, Adobe, Macromedia and Microsoft Authoring Tools

\subsection[experience]{Experience}

\subsubsection[technology-director-csm-at-gsw]{{\bf Technology Director,
CSM} at \useURL[url7][http://gsw-w.com][][GSW]\from[url7]}

{\em February 2013 - Present}

Manage team of developers on a variety of mobile and web projects across
multiple brands and strategies. Key component in discovery of new
technologies and their applicability to brands. Leader in pitch work,
strategic planning, and high level technical discussions with partners
and clients. Client and team technology educator.

\subsubsection[senior-multimedia-developer-at-gsw]{{\bf Senior
Multimedia Developer} at
\useURL[url8][http://gsw-w.com][][GSW]\from[url8]}

{\em June 2011 - February 2013} (1 year 9 month)

Interactive web, mobile, and tablet experiences for a variety of
pharmaceutical brands. Developed iPad and Android tablet sales pieces.
Led teams building rich informational applications for the web in HTML5
and Flash, and in a variety of mobile platforms. Coached and trained
other developers to increase the team's productivity and effectiveness.
Was trained and mentored toward management roles.

\subsubsection[jesuit-novice-at-society-of-jesus]{{\bf Jesuit Novice} at
\useURL[url9][http://jesuit.org][][Society of Jesus]\from[url9]}

{\em August 2010 - March 2011} (7 months)

Rigorous prayer & study life with an dual focus on contemplative prayer
and applying that lifestyle through a variety of social apostolates
including teaching in a Catholic grade school and pastoral care to
terminally ill hospice patients. Studis included a survey of the history
of religious life, the foundational documents of the Society of Jesus,
and both theory and practice at the art of communal life.

\subsubsection[flash-developer-at-empathy-lab]{{\bf Flash Developer} at
\useURL[url10][http://www.epam.com/empathylab.html][][Empathy
Lab]\from[url10]}

{\em July 2009 - July 2010} (1 year)

Developed interactive games, microsites, user experiences, and
animations for companies like Sprout, Lexmark, Sesame Street and many
more. Developed a large scale streaming video application built off
Adobe's Open Source Media Framework, Akamai's Open Video Player,
utilizing PureMVC and a variety of custom made tracking tools for
integrating Omniture, Comscore, Google Analytics, and others.

\subsubsection[senior-new-media-developer-at-moxie-interactive]{{\bf Senior
New Media Developer} at
\useURL[url11][http://moxieinteractive.com][][Moxie
Interactive]\from[url11]}

{\em August 2007 - July 2009} (2 years)

Developed frameworks for rich landing pages, advertising campaigns, and
product spotlights. Built rich media banners, websites, social
networking applications and landing pages for clients such as Coke, Home
Depot, Verizon, Verizon Wireless, Fox, UPS and Maybelline. Lead and
architected large-scale web marketing campaigns while managing the
development team.

\subsubsection[multimedia-specialist-at-pango-media]{{\bf Multimedia
Specialist} at \useURL[url12][http://pangomedia.com][][Pango
Media]\from[url12]}

{\em June 2006 - August 2007} (1 year 4 months)

Responsible for management, design and development of web sites,
interactive CDs, mobile and desktop applications, Flash, and print
materials.

\subsubsection[developer-at-medical-animatics-inc]{{\bf Developer} at
\useURL[url13][http://www.medicalanimatics.com/][][Medical Animatics,
Inc]\from[url13]}

{\em September 2005 - June 2006} (10 months)

Developed ongoing Flash applications and server-side scripting &
database design. Designed digital and print media for use in large scale
products.

\subsubsection[nuclear-electronics-technician-at-us-navy]{{\bf Nuclear
Electronics Technician} at
\useURL[url14][http://www.netc.navy.mil/nnptc/][][US Navy]\from[url14]}

{\em March 2000 - June 2001} (1 year 4 Months)

Trained as a nuclear reactor operator of the Naval surface fleet.

\subsection[skills-expertise]{Skills & Expertise}

Those things which enjoy routine usage in my daily work are denoted with
a \high{†} symbol.

\subsubsection[programming-languages]{Programming Languages}

\startitemize[packed]
\item
  \useURL[url15][http://developer.mozilla.org/en/JavaScript][][JavaScript]\from[url15]\high{†}
\item
  \useURL[url16][http://php.net][][PHP]\from[url16]\high{†}
\item
  \useURL[url17][http://python.org][][Python]\from[url17]
\item
  \useURL[url18][http://ruby-lang.org][][Ruby]\from[url18]
\stopitemize

\subsubsection[markuptemplating-languages-preprocessors]{Markup/Templating
Languages & Preprocessors}

\startitemize[packed]
\item
  \useURL[url19][http://coffeescript.org][][CoffeeScript]\from[url19]
\item
  \useURL[url20][http://www.w3.org/Style/CSS/Overview.en.html][][CSS]\from[url20]\high{†}
\item
  \useURL[url21][http://haml.info][][Haml]\from[url21]
\item
  \useURL[url22][http://handlebarsjs.com][][Handlebars.js]\from[url22]
\item
  \useURL[url23][http://developers.whatwg.org][][HTML]\from[url23]\high{†}
\item
  \useURL[url24][http://lesscss.org][][LESS]\from[url24]
\item
  \useURL[url25][http://daringfireball.net/projects/markdown][][Markdown]\from[url25]\high{†}
\item
  \useURL[url26][http://mustache.github.com][][Mustache]\from[url26]
\item
  \useURL[url27][http://sass-lang.com][][Sass]\from[url27]\high{†}
\stopitemize

\subsubsection[frameworks-apis]{Frameworks & APIs}

\startitemize[packed]
\item
  \useURL[url28][http://documentcloud.github.com/backbone][][Backbone.js]\from[url28]
\item
  \useURL[url29][http://compass-style.org][][Compass]\from[url29]\high{†}
\item
  \useURL[url30][http://codeigniter.com][][CodeIgniter]\from[url30]
\item
  \useURL[url31][http://developers.google.com/maps][][Google Maps
  API]\from[url31]
\item
  \useURL[url32][http://jquery.com][][jQuery]\from[url32]\high{†}
\item
  \useURL[url33][http://meteor.com][][Meteor]\from[url33]
\item
  \useURL[url34][http://requirejs.org][][Require.js]\from[url34]
\item
  \useURL[url35][http://rubyonrails.org][][Ruby on Rails]\from[url35]
\item
  \useURL[url36][http://dev.twitter.com][][Twitter API]\from[url36]
\item
  \useURL[url37][http://wordpress.org][][Wordpress]\from[url37]
\stopitemize

\subsubsection[software-tools]{Software & Tools}

\startitemize[packed]
\item
  \useURL[url38][http://www.adobe.com/products/creativesuite.html][][Adobe
  Creative Suite]\from[url38]\high{†}
\item
  \useURL[url39][http://aws.amazon.com][][Amazon Web
  Services]\from[url39]
\item
  \useURL[url40][http://apache.org][][Apache]\from[url40]\high{†}
\item
  \useURL[url41][http://developer.apple.com][][Apple XCode]\from[url41]
\item
  \useURL[url42][http://git-scm.com][][Git]\from[url42]\high{†}
\item
  \useURL[url43][http://atlassian.com/software/jira][][JIRA]\from[url43]
\item
  \useURL[url44][http://apple.com/macosx][][Mac OS
  X]\from[url44]\high{†}
\item
  \useURL[url45][http://mysql.com][][MySQL]\from[url45]
\item
  \useURL[url46][http://johnmacfarlane.net/pandoc][][Pandoc]\from[url46]
\item
  \useURL[url47][http://rvm.beginrescueend.com][][rvm]\from[url47]\high{†}
\item
  \useURL[url48][http://www.sublimetext.com][][Sublime Text]\from[url48]
\item
  \useURL[url49][http://svn.apache.org][][Subversion]\from[url49]
\item
  \useURL[url50][http://tmux.sourceforge.net][][tmux]\from[url50]
\item
  \useURL[url51][http://ubuntu.com][][Ubuntu Linux]\from[url51]
\item
  \useURL[url52][http://www.vim.org][][Vim]\from[url52]\high{†}
\item
  \useURL[url53][http://yeoman.io][][Yeoman]\from[url53]
\item
  \useURL[url54][http://www.zsh.org][][zsh]\from[url54]
\stopitemize

\subsection[education]{Education}

\useURL[url55][http://iupui.edu][][Indiana University]\from[url55],
School of Informatics MS, Media Arts and Sciences, 2005 - 2006

\useURL[url56][http://iupui.edu][][Indiana University]\from[url56],
School of Informatics BS, Media Arts and Sciences, 2002 - 2004

\subsection[honors-and-awards]{Honors and Awards}

\startitemize[packed]
\item
  {\em Atlanta Addy Awards 2009}
  \startitemize[packed]
  \item
    Gold: Website Flash, Online (Fight for Gotham City)
  \stopitemize
\item
  {\em IMA Awards 2008}
  \startitemize[packed]
  \item
    Outstanding Achievement Award: Telecommunications category (Fight
    For Gotham City)
  \stopitemize
\item
  {\em Create Awards 2008}
  \startitemize[packed]
  \item
    Silver Award: Interactive Web Elements, Banners/Tiles category (20th
    Century Fox Jumper DVD)
  \stopitemize
\item
  {\em Atlanta Addy Awards 2008}
  \startitemize[packed]
  \item
    Silver: Interactive Media, Online (The Home Depot Kitchens)
  \item
    Silver: Interactive Media, Online (Verizon Wireless Oddcast/Pop,
    Lock and Send)
  \item
    Bronze: Interactive Media, Online (The Home Depot Holiday)
  \stopitemize
\item
  {\em The Webby Awards 2008 }
  \startitemize[packed]
  \item
    Official Honoree: Interactive/Rich Media Advertising:
    Business-to-Consumer (Verizon Wireless Next Phones Now)
  \stopitemize
\item
  {\em Atlanta ADDYs ShowSouth 2007}
  \startitemize[packed]
  \item
    Silver: Microsite (The Home Depot Holiday)
  \item
    Silver: Website (Verizon Wireless Motorola Q Launch)
  \stopitemize
\item
  {\em Atlanta AMA AMY Awards 2007}
  \startitemize[packed]
  \item
    Winner: Web/Interactive Use of Multimedia/New Media (Verizon
    Wireless Chocolate Launch)
  \item
    Winner: Web/Interactive Generating Online Sales (The Home Depot
    Holiday Microsite)
  \stopitemize
\stopitemize

\subsection[interests]{Interests}

\startitemize[packed]
\item
  Being a dad and spending time with my family
\item
  \useURL[url57][http://map.tomasino.org/][][Creating
  worlds]\from[url57] for books and games
\item
  Playing \useURL[url58][http://boardgamegeek.com/user/tomasino][][board
  and card games]\from[url58] (and video games, too)
\item
  Watching and contributing to Open Source Software
\stopitemize

 ©2013 \useURL[url59][http://jamestomasino.com/resume][][James
Tomasino]\from[url59]. All rights reserved. Direct contact only desired
(no~recruiters please).

\stoptext
